Analysis of the included studies

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed mdthemes package

```{r echo=FALSE, include=FALSE}
#' load packages
library('tidyverse')
library('ggthemes')
library('mdthemes')
library('scales')
library('janitor')
library('countrycode')
library('bib2df')
library('conflicted')
library('ggwordcloud')

>>>>

```{r echo=FALSE, include=FALSE}
#' load packages
library('tidyverse')
library('ggthemes')
library('scales')
library('janitor')
library('countrycode')
library('bib2df')
library('conflicted')
library('ggwordcloud')
